What is disputed on the web?

### 2010-02-02 papers/wicow_claimfinder/claimfinder.tex
two superficial changes: themselves -> herself capitalize United States

We identify disputed claims by searching for lexical patterns such as ``the misconception that'' (Section~\ref{findingclaims}). For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim. In Figure~\ref{templates-fig} we list some of the patterns we used. In practice, many of the strings that match such a pattern are not well-formed disputed claims. We use a statistical classifier to select only those strings that appear to make a well-formed claim.

@@

\begin{itemize}
 \item {\bf Obama:} Barack Obama is not a topic of dispute until 2004 when he spoke at the Democratic convention. His level of controversy then peaked in 2008, in the run up to the November 2008 US presidential elections.
 \item {\bf God:} God is always a controversial topic. We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawkins2006}.
 \item {\bf Iraq:} Spikes seem to correspond to the initial invasion in 2003 and the surge in 2007.
 \item {\bf Israel:} The Gaza conflict of 2007 caused a big spike.  
\end{itemize}

@@

Figure~\ref{cluster-figure} shows the most frequently occurring word clusters that we found for each noun. For each cluster, the count is the number of claims about that noun that contain all of the words. Most of these will make sense to people who have been following news in the United States. For example, we see that disputed claims about Obama often talk about his Nobel Prize or his birth certificate, and we see that President Ahmadinejad of Iran did not actually say that Israel should be wiped off the map (which the authors had not previously realized). Some of the word clusters are not particularly interesting; for example many claims talk about the united states, even when that is not an important part of what is disputed.

>>>>

We identify disputed claims by searching for lexical patterns such as ``the misconception that'' (Section~\ref{findingclaims}). For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author herself disputes this claim. In Figure~\ref{templates-fig} we list some of the patterns we used. In practice, many of the strings that match such a pattern are not well-formed disputed claims. We use a statistical classifier to select only those strings that appear to make a well-formed claim.

@@

\begin{itemize}
 \item {\bf Obama:} Barack Obama is not a topic of dispute until 2004 when he spoke at the Democratic convention. His level of controversy then peaked in 2008, in the run up to the November 2008 US presidential elections.
 \item {\bf God:} God is always a controversial topic. We theorize that the spike in 2006 may relate to the 2006 publication of the Richard Dawkins book ``the God Delusion''\cite{Dawkins2006}.
 \item {\bf Iraq:} Spikes seem to correspond to the initial invasion in 2003 and the surge in 2007.
 \item {\bf Israe:} The Gaza conflict of 2007 caused a big spike.  
\end{itemize}

@@

Figure~\ref{cluster-figure} shows the most frequently occurring word clusters that we found for each noun. For each cluster, the count is the number of claims about that noun that contain all of the words. Most of these will make sense to people who have been following news in the United States. For example, we see that disputed claims about Obama often talk about his Nobel Prize or his birth certificate, and we see that President Ahmadinejad of Iran did not actually say that Israel should be wiped off the map (which the authors had not previously realized). Some of the word clusters are not particularly interesting; for example many claims talk about the United States, even when that is not an important part of what is disputed.
